mdsR: A Suite of Functions for Working with Nursing Home Minimum Data Set Assessments.
===============

[![CRAN version](https://www.r-pkg.org/badges/version/MDS)](https://cran.r-project.org/package=mdsR)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/mdsR)](https://cran.r-project.org/package=mdsR)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Overview  
The following package is a collection of R functions and example datasets to which will assist in checking, testing, formatting and generating preliminary results from Minimum Data Set Assessments.  

# Installation  
```{r, eval=F}
# install from CRAN: (Not implemented yet)
install.packages("mdsR")

# Or the the development version from GitHub:
# install.packages("devtools")
devtools::install_github("kmcconeghy/mdsR")
```
This package relies heavily on the suite of packages and programming termed "Tidyverse", e.g. "dplyr", "lubridate", that must be installed for proper functioning.  

# Usage  
The primary goal of this package is to provide a toolkit for researchers who commonly work with MDS data. The included functions will check MDS data against a standard dictionary, confirm proper variable labelling, format and do some typical reshaping and data analyses common to many projects.  

# Simple Example  
```{r, include=F}
library(mdsR, quietly = T, warn.conflicts = F)
library(tidyverse, quietly = T, warn.conflicts = F)
```

### Example data  

# Vignettes  
Several companion documents have been written to assist interested readers with the background and use of the package. We suggest you start here:
[Introduction to mdsr](https://kmcconeghy.github.io/mdsR/01-introduction.html) or if the package is installed:  
```{r, eval=F}
devtools::vignette("01-Introduction", "mdsR")
```

# Latest Version Updates  

This package is in the early stages of development. Many features may change in a short amount of time.  

# Future Goals for MDS   

Under construction  

# Important References   

Under construction  

# Authors  
Kevin W. McConeghy, Pharm.D, M.S., Brown University School of Public Health, Dept. Health Services Research  

# Acknowledgements  
The programming was derived with guidance and example code from the following individuals.  

* 
