---
title: "mdsR: Nursing Home Assessment Background"
author: "Kevin W. McConeghy"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flumodelr: 02-Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
library(mdsR)
library(tidyverse)
```

## Introduction  

A primary purpose of this package is to check raw MDS data, format and prepare it for a 'tidy' analytical dataset.  

The following sections demonstrate examples:  

## Test that mds data.frame is canonical  

For the package to work it must: 

 1) Be a 'data.frame', 'tbl' class object.  

 2) Have named variables consistent with mdsR internal data dictionary  
 
### Calling mdsR internal data  

Most functions will call an internal dictionary, when checking whether variables are properly formatted etc. The guides mdsR to what kind of a variable a column is, what to label it, whether it is a common mds ResDAC item or something Brown generates for its own server purposes etc. It only works if the data frame is set-up properly.   

#### Test example file  

```{r }
mds_dta <- cars
mds_chkmds(mds_dta)
```

## Check variables for formatting  


## Brown specialty variables  

